### 2018-07-05 paper/sphinxes.tex
Adds Sphinxes extension description

\subsection{The Sphinxes extension}

\dots

>>>>

\subsection{The Sphinxes extension for sets of nodes}

\NewAlgorithm{\Enc}{Enc}

We will now extend Sphinx: instead of providing only \(d_{i+1}\) in 
\(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) of 
\(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

In Sphinx we denoted the public key for layer \(i\) as \(\pk_i\).
Since we have \(m\) alternative nodes with different keys, let us denote them 
by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).

We extend the header to a quadruple \((\alpha_i, C_i, \beta_i, \gamma_i)\), 
where \(\alpha_i, \beta_i, \gamma_i\) are the same as before.
We let the shared secret \(s_i\) be chosen uniformly randomly instead of being 
computed as \(\alpha_i^{\sk_i}\).
We now compute one shared secret per alternative node, \ie \(s_i^{(j)} = 
  \alpha_i^{\sk_i^{(j)}}\) for \(1\leq j\leq m\).
Then \(C_i = c_i^{(1)}\concat \dotsb\concat c_i^{(m)}\) is the concatenation of 
ciphertexts \(c_i^{(j)} = \Enc[_{s_i^{(j)}}][s_i]\), where \(\Enc\) is 
\iac{SKE} algorithm and each ciphertext contains the shared secret \(s_i\) 
encrypted under the individual keys \(s_i^{(j)}\).
